Need a good title. Submit to Methods of Ecology and Evolution or Evolutionary Biology

### 2018-04-01 main.tex
temp pushing

Phylogenetic comparative methods have been widely used to study species relativeness problems.
Phylogenetic models aim to find parsimonious methods that can be used to link ecological phenomena with evolutionary processes by incorporating the historical relationships shared across species via phylogenetic (evolutionary) trees. 
\ml{parsimonious can be a confusing word here}
Although such models attempt to account for species correlations, they often make strong and over-simplified assumptions of the evolutionary process. 
Decades of work have created various different methods that enables researchers to incorporate phylogenetic effects in analyzing species relativeness applications.
But many challenges remain.
In particular, accounting for phylogenetic effects in high dimensional systems is always challenging, especially for models incorporating multiple forms of phylogenetic effects, and especially with large phylogenies where computation powers are limited.
\ml{Define phylogenetic effects. PE can mean a lot of different things (see Pagel's tree transformation). What we mean here is strictly phylogenetic signal-- extent to which trait/response values are statistically related to phylogeny.}
Ignoring phylogenetic effects/signals can be problematic both biologically and statistically \citep{felsenstein1985phylogenies, li2017statistical} -- in such cases, researchers often use simpler models accounting for minimal phylogenetic signals by limiting at the individuals level and neglect additional phylogenetic signals present in the system.

>>>>

Phylogenetic comparative methods have been widely used to study the relationships among traits of species within an evolutionary lineage.
These approaches aim to find parsimonious models that link traits and ecological phenomena with evolutionary processes by incorporating the historical relationships shared among taxa as represented by phylogenetic (evolutionary) trees. 
Although such models attempt to account for correlations among species, \ml{they often make strong and over-simplified assumptions of the evolutionary process.REWRITE THIS.. something like complicated and comp inefficient and often neglict.} 
Decades of work have created various different methods that enables researchers to incorporate phylogenetic effects in analyzing species relativeness applications.
But many challenges remain.
In particular, accounting for phylogenetic effects in high dimensional systems is always challenging, especially for models incorporating multiple forms of phylogenetic effects, and especially with large phylogenies where computation powers are limited.
\ml{Define phylogenetic effects. PE can mean a lot of different things (see Pagel's tree transformation). What we mean here is strictly phylogenetic signal-- extent to which trait/response values are statistically related to phylogeny.}
Ignoring phylogenetic effects/signals can be problematic both biologically and statistically \citep{felsenstein1985phylogenies, li2017statistical} -- in such cases, researchers often use simpler models accounting for minimal phylogenetic signals by limiting at the individuals level and neglect additional phylogenetic signals present in the system.
